\documentclass{resume}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Rahmathullah M}
% ------ Address --------------------------------------------------------

\address{UI Developer\\
  Tata Consultancy Services, London, UK\\
  {\em Ph:} (+91)-9895 63 9860}{
  {\em email:} \mbox{\small\tt rahmathm1@gmail.com}\\
  {\em github:} \mbox{\small\tt github.com/rahmathm1}\\
  {\em linkedin:} \mbox{\small\tt linkedin.com/in/rahmathm1}}

\begin{document}
\maketitle

% --------- Research ----------------------------------------------------

%\begin{category}{Research interests}
%  \citemnobullet NoSQL databases, Android application development,
%  Test Driven Development, development of Ruby Gems, Design Patterns.
%\end{category}

\begin{category}{Technical Skills}
  \citembullet {\it Programming Languages}: JavaScript, TypeScript, HTML5, SASS, Java.
  \citembullet {\it Frameworks}: Angular 1 \& 2+, VueJS, ReactJS, Redux(NGRX), ASP.Net, Spring Boot.
  \citembullet {\it DevOps}: Docker, Kubernetes(AWS EKS).
  \citembullet {\it Operating Systems}: Linux, Mac OSX, Microsoft Windows.
  \citembullet {\it Others}: Micro-frontends, Redux, SMACSS, Photoshop, Zeplin.
\end{category} 

% -------- Work experience --------------------------------------------

\begin{category}{Work Experience}
  
  \citem{Tata Consultancy Services}
  \citemnobullet \textbf{Assistant Consultant} \hfill \textbf{Apr 2018 -- present}
  \citemnobullet Tata Consultancy Services Limited is an Indian multinational information technology service, consulting company headquartered in Mumbai, Maharashtra. It is part of the Tata Group and operates in 46 countries.
  \begin{itemize}
  \item \textbf{Idea Tool} (Apple, US) : A single page application developed in Angular 6, which helps Apple employees to collaborate and innovate ideas. {\em Angular6, Spring Boot}. \textbf{Role}: {\em Full-stack Developer}. 
  \item \textbf{Analytics Tool} (Apple, US) : A Angular 4 application to generate various charts and reports based on the test data from various testing devices. {\em Angular4 with Ngrx}. \textbf{Role}: {\em Front End Developer}. 
  \item \textbf{NullIsland} (Apple, US) : An Angular 8 application for managing jobs for device testing and to generate test reports from these testing devices. Backend is developed in Spring Boot. {\em Angular4, Spring Boot}. \textbf{Role}: {\em Full-stack Developer(Java \& Angular)}. 
  \item \textbf{Career Development Portal} (Apple, UK) : React application that helps employees to self evaluate themselves and helps them to track their career goals. {\em ReactJS \& Redux}. \textbf{Role}: {\em Front End Developer}. 
  \item \textbf{Pithos Apps} (Apple, UK) : Plugin development for Grafana instances to monitor system performances and metrices. Containerization and deployment of these instances into AWS EKS. {\em Grafana, Kubernetes \& React}. \textbf{Role}: {\em DevOps \& UI Developer}.   
  \end{itemize}

  
  \citem{QBurst Technologies Pvt Ltd}
  \citemnobullet \textbf{Sr. Software Engineer} \hfill \textbf{Dec 2014 -- Mar 2018}
  \citemnobullet QBurst is a software solutions and consulting company with offices across the globe.
\\The company has been recognized as one of the top mobile app developers in India by Clutch (erstwhile SourcingLine) and ranked 36th in Deloitte Technology Fast 50 India (2013). QBurst features in the Deloitte Technology Fast 500 Asia Pacific ranking for 2012, 2013, and 2014.
  \begin{itemize}
  \item \textbf{Ticket Booking System} : A single page application developed in Angular 4, which helps user to book flight tickets. {\em Angular4, Angular Material, SCSS with SMACSS, ng-cli}. \textbf{Role}: {\em Front End Engineer}. 
  \item \textbf{Foaps - Live Menu} : A Cordova application developed in VueJS, which helps people to access menus from anywhere. {\em VueJS, Framework7, Cordova, SASS with SMACSS, Webpack}. \textbf{Role}: {\em Front End Developer}. 
  \item \textbf{Profiles Project} : The provider profile module of public site of NYU Langone Medical Center, med.nyu.edu. Developed a timeline view of the providers researches. {\em D3.Js, SASS with SMACSS, BEM }. \textbf{Role}: {\em Front End Developer}. 
  \item \textbf{Lead Site} : Lead site is developed on Drupal CMS, using D3.Js for illustrating economic costs of childhood lead exposure in low-and middle-income countries research. {\em D3.Js, CSS3 }. \textbf{Role}: {\em Front End Developer}. 
  \item \textbf{DTI Data Maintanance Tool} : A tool to manage contents of nyulangone.org. Project strictly followed Ajile methodologies. {\em VueJS, jQuery, Bootstrap, SASS, JIRA }. \textbf{Role}: {\em Front End Developer}. 
  \item \textbf{JIGSAW Framework} : The ultimate aim of this project is to develop a framework using which, end user can develop  or customize module as they need, easily. The project has modules like Employees, Orders, Customers, etc. Developed using {\em TypeScript, KnockoutJs and .Net MVC}. \textbf{Role}: {\em Developer}.
  \end{itemize}

  \citem{CYBOSOL(Nuevalgo Solutions Pvt Ltd)}
  \citemnobullet \textbf{Software Engineer} \hfill \textbf{Nov 2012 -- Dec 2014}
  \citemnobullet CYBOSOL(Nuevalgo solutions) is a service oriented company set up by a team of highly-experienced technology professionals. \\CYBOSOL practices Extreme Programming and Continuous
  Delivery to rapidly ship quality software. Ruby on Rails, HTML5, PHP, .Net, Android and iOS are the technologies of choice.
  \begin{itemize}
  \item \textbf{EBook Reader} : A bilingual SPA which uses {\em Angular JS, jQuery, EPub.js, Bing Translation, Facebook API, Google Plus, Twitter API integrations}. \textbf{Role}: {\em Front End Developer}.  
  \item \textbf{Online Store} : A social commerce application which allow users to join together using their social media network and get good deals by utilizing collective power of groups buying. The initial target will be UAE, Saudi Arabia and India. Developed using {\em BackboneJS, jQuery and RESTFul API}. \textbf{Role}: {\em Front End Developer}.
  \item \textbf{IdealHomes Realestate}: Android and iOS using PhoneGap, Property management system for property Listing, contact the agent, request Viewing, image gallery, etc. Using {\em Phonegap, Backbone.js, jQuery, HTML5, CSS3}. \textbf{Role}: {\em Front End Developer}.
  \item \textbf{iMenu} : A Point of sales application for an ERP Product. Developed using {\em Phonegap, Backbone.js, jQuery, HTML5, CSS3}. \textbf{Role}: {\em Front End Developer}.
  \item \textbf{Taskforces ERP Mobile Version} : A mobile version of an existing desktop ERP product, named Taskforces ERP. Includes. HR and Finance Modules of the desktop app. Using{\em
      Phonegap, jQuery Mobile, PHP for API}. \textbf{Role}: {\em Front End Developer}. 
  \end{itemize}
\end{category}

% -------- Awards & Honours ---------------------------------------

\begin{category}{Awards \&\\ Recognition}
  \citem{``Award for Technical Excellence''}, {\em Apple, TCS Kochi}. \hfill \textbf{2015}
  \citem{``I\textsuperscript{st} - Hacknight''}, {\em QBurst Kochi}. \hfill \textbf{2015}
  \citem{``I\textsuperscript{st} - GDG Dart Flight School CodeLab''}, {\em GDGCochin}. \hfill \textbf{2014}
  \citem{``Star of Nuevalgo''}, {\em Nuevalgo Solutions Private Limited}. \hfill \textbf{2013}
  \citem{``Special Momento''}, {\em  National Conference, Fisat, Angamaly}. \hfill \textbf{2012}
  %\citem{``II\textsuperscript{nd} -  Web  Designing''}, {\em Fisat Angamaly}. \hfill \textbf{2012}
  %\citem{``III\textsuperscript{rd} -  Web  Designing''}, {\em  Naipunnya  Institute  of  Management  and  Information  Technology, Pongam}. \hfill \textbf{2012}
\end{category}

% ------- Education ---------------------------------------------------

\begin{category}{Education}
  \citem{Master of Computer Applications (72\%)} \hfill \textbf{2009 -- 2012}
  \citemnobullet Federal Institute of Science And Technology, Kerala.
  \citem{Bachelor  Of  Computer  Science  (70\%)} \hfill \textbf{2005 -- 2008}
  \citemnobullet  EMEA College of Arts \& Science, Kondotty, Kerala.
  \citem{Higher Secondary Education (67\%)} \hfill \textbf{2003 -- 2005}
  \citemnobullet PPM Higher Secondary School, Kondotty, Kerala.
  \citem{SSLC (74\%)} \hfill \textbf{2003}
  \citemnobullet PPM Higher Secondary School, Kondotty, Kerala.\end{category}
  
% -------- Opensource -------------------------------------------

%\begin{category}{Opensource}
%  \citemnobullet List of major opensource contributions. Refer GitHub for source code.
%  \citembullet \textbf{time\_diff}: Ruby Gem which calculates the difference between two times.
%  \citembullet \textbf{OrphanRecords}: Ruby Gem which show/delete the orphan records in your Rails application
%  \citembullet \textbf{who-is-next}: An android application which helps us to keep in touch with friends and relatives.
%\end{category}

% -------- Reference --------------------------------------------

%\begin{category}{Reference}
%  \citemnobullet \\
%  \begin{tabular}{ll}Shihabudheen PK&Ajith Khan\\
%    Director&Associate Architect\\
%    WinWius Techno Solutions Pvt Ltd&MicroSoft Technologies\\
%    Kochi&QBurst\\
%    Email: \mbox{\small\tt shihab@winwius.com}&Email: \mbox{\small\tt ajithkhan@qburst.com}\\
%    Ph: (+91)-9961-429066&Ph: (+91)-9744-887272
%  \end{tabular}
%\end{category}
\end{document}
